\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-21 paper.tex
stated section evaluator

    The parser of type \textit{p} takes a state represented as a string ready to be parsed and returns a list containing the value of type \textit{p} parsed from the string and a state represented again as a string that is yet to be parsed. Since a parser may not consume all of its input string, the unconsumed suffix of the input must be returned along with the prefix of the input. As a result, the outcome of a parser must be a list enclosing consumed and unconsumed part of the input string. Additionally, the case when an empty list is returned is treated as a failure \cite{pearls}. On the other hand, an non-empty list is marked as a success. Lets take into consideration a straightforward parser for multiplication operations.

    \begin{center}
        \textbf{data} Expr = Const \textit{Int} $\vert$ Multi \textit{Expr} \textit{Expr} 
    \end{center}

    Next, lets create a parser of type Expr.

    \begin{center}
        parseExpr :: \textbf{Parse} \textit{Expr} 
    \end{center}

    The following examples take as input the state defined as a string.

    \begin{lstlisting}[language=Haskell]
        parseExpr "27 or twentyseven" = [(Const 27, " or twentyseven")] 
        parseExpr "twentyseven"       = []
    \end{lstlisting}

    For simplicity, the focus will remain on parsers that either fail and return an empty list of results, or succeed and return a singleton list.

@@

@@

    \subsection{Repetition}

    At the moment the isword parser

@@

>>>>

    The parser of type \textit{p} takes a state represented as a string ready to be parsed and returns a list containing the value of type \textit{p} parsed from the string and a state represented again as a string that is yet to be parsed. Since a parser may not consume all of its input string, the unconsumed suffix of the input must be returned along with the prefix of the input. As a result, the outcome of a parser must be a list enclosing consumed and unconsumed part of the input string. Additionally, the case when an empty list is returned is treated as a failure \cite{pearls}. On the other hand, an non-empty list is marked as a success.

@@

    \noindent Additionally, on section 7 the created parser will be evaluated with the usage of the \textbf{State} and \textbf{Exception} monads.

@@

@@

    \section{Evaluator}

    In this section, the outcome of \textbf{my\textunderscore parser} will be evaluated with the utilization of the \textit{state} and \textit{exception} monads. These monads have not been imported from the Haskell language but have been re-created together with their accompanying monadic behavior. In addition, the approach taken to evaluate each statement of the simple programming language is observed and the helper monadic functions that were constructed are discussed in detail. Let's dive in.

    \subsection{State}

    \subsection{Exception}

    \subsection{Get and Put}
